---
title: "Geographic Trends Survey Results"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

#read in data
geographic_trends_data=read_csv("FinalCleanedData.csv")
```

# Overview {data-orientation=columns}

## Column {data-width=300}

### Questions

The questions that this dashboard will answer are the following: 

* Where are out students going (region)?
* What are the salary differentials by region?
* What types of jobs (By company) are students getting by region?  Are bank and consulting jobs in Chicago and NYC?
* What are the top 3-5 job categories (by company) by city (Chicago, Cincinnati, Columbus, Cleveland)?


## Column {data-width=300}

### Insights

Written insights and links to other pages that support conclusions
   

# Placement {data-orientation=columns}

### Where are students going?

```{r,echo=FALSE}

```



# Salary {data-orientation=columns}

### Salary differentials by region

```{r,echo=FALSE}

```


# Company Composition {data-orientation=columns}

### Biggest City

What types of jobs (By company) are students getting by region?  Are bank and consulting jobs in Chicago and NYC?

```{r}

```


### Top 3-5 Companies by City

What are the top 3-5 job categories (by company) by city (Chicago, Cincinnati, Columbus, Cleveland)?

```{r}

```

