---
title: "Geographic Trends Survey Results"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT, 
               ggplot2, 
               maps,
               ggrepel, #for better tables
               dplyr,
               uscities
               )

#read in data
geographic_trends_data=read_csv("FinalCleanedData.csv")
```

# Overview {data-orientation=columns}

## Column {data-width=300}

### Questions

The questions that this dashboard will answer are the following: 

* Where are out students going (region)?
* What are the salary differentials by region?
* What types of jobs (By company) are students getting by region?  Are bank and consulting jobs in Chicago and NYC?
* What are the top 3-5 job categories (by company) by city (Chicago, Cincinnati, Columbus, Cleveland)?


## Column {data-width=300}

### Insights

* Top 4 placement cities for students graduating Miami University FSB is Chicago, Cincinnati, Columbus, and Cleveland. 
* On average, the top paying city is NYC, however it is shocking that it is just over $67,000.  The top paying state is California with New York to shortly follow. 
* Accounting and Finance are the top type of jobs in Chicago and NYC. Chicago does have a handful of alumni doing Consulting at West Monroe Partners.
* EY and Deloitte is the in the top 3 companies for Cincinnati, Chicago and Cleveland.
   

# Placement {data-orientation=columns}

## Column {data-width=450}

### Where are students going in the USA?


```{r,echo=FALSE}

# fix NYC coordinates 
# Define the true coordinates of New York City
nyc_latitude <- 40.7128
nyc_longitude <- -74.0060

# Fill the rows where survey_city is 'newyorkcity' with the true coordinates
geographic_trends_data <- geographic_trends_data %>%
  mutate(latitude = ifelse(survey_city == 'newyorkcity', nyc_latitude, latitude),
         longitude = ifelse(survey_city == 'newyorkcity', nyc_longitude, longitude))

top_cities <- geographic_trends_data %>% 
  group_by(survey_city) %>%
  summarize(listing_count = n()) %>%
  arrange(desc(listing_count)) %>%
  top_n(10, listing_count)

# Subset the geographic_trends_data to only include the top 10 cities
geographic_trends_subset <- geographic_trends_data %>%
  filter(survey_city %in% top_cities$survey_city)

# Get a map of the United States
us_map <- map_data("world")

ggplot() +
  geom_polygon(data = us_map, aes(x=long, y = lat, group = group), fill="white", alpha=0.1) +
  geom_path(data = us_map, aes(x = long, y = lat, group = group), color = "gray", size = 0.5) +  # Add state borders
  geom_point(data = geographic_trends_data, aes(x = longitude, y = latitude, alpha = 0.2), color = 'purple') +  
  coord_cartesian(xlim = c(-110, -65), ylim = c(25, 50) ) + 
  geom_text(data = geographic_trends_subset, aes(x = longitude, y = latitude, label = survey_city), hjust = 0.1, vjust = 0.1, size = 2.5) +
  scale_alpha(guide = "none") +
  theme_minimal() 
```

## Column {data-width=150}

### Top 10 Placement Cities

```{r,echo=FALSE}
data <- geographic_trends_data %>%
  filter(!is.na(survey_city)) %>%  # Remove rows where survey_city is NULL
  group_by(survey_city) %>%
  summarize(count = n()) %>%
  arrange(-count, survey_city)

custom_column_names <- c("City", "Number of Students")


datatable(data, rownames = FALSE, extensions = 'Buttons', colnames = custom_column_names,
          options = list(dom = 'Bfrtip',
                         buttons = c('copy', 'csv', 'excel')
                         ),
          filter = list(position = 'bottom',
                        clear = FALSE, plain = TRUE
                        )
          )
```

# Salary {data-orientation=columns}

## Column {data-width=300}

### Average Salary per State

```{r,echo=FALSE}
datasal <- geographic_trends_data %>%
  filter(survey_salary > 0) %>%
  group_by(survey_state) %>%
  filter(n() >= 10) %>%
  summarize(
    avgSalary = scales::dollar(mean(survey_salary)),  # Format as currency
    rowCount = n()  # Count of rows per group
  ) %>%
  arrange(desc(avgSalary), survey_state)

custom_column_names <- c("City", "Company", "Number of Students")

datatable(datasal, rownames = FALSE, extensions = 'Buttons', colnames = custom_column_names,
          options = list(dom = 'Bfrtip',
                         buttons = c('copy', 'csv', 'excel')
                         ),
          filter = list(position = 'bottom',
                        clear = FALSE, plain = TRUE
                        )
          )

```

## Column {data-width=300}
### Average Salary for Top 10 locations

```{r, echo=FALSE}
library(dplyr)
library(ggplot2)

datasal <- geographic_trends_data %>%
  filter(!is.na(survey_city)) %>% 
  filter(survey_salary > 0) %>%
  group_by(survey_city) %>%
  filter(n() >= 10) %>%
  summarize(
    avgSalary = scales::dollar(mean(survey_salary)),  # Format as currency
    rowCount = n()  # Count of rows per group
  ) %>%
  arrange(desc(avgSalary), survey_city)

top_cities <- datasal %>%
  arrange(desc(rowCount)) %>%
  top_n(10, rowCount)


# Create a graph with the specified requirements
ggplot(top_cities, aes(x = rowCount, y = avgSalary)) +
  geom_point(color = "purple") +
  geom_text(aes(label = survey_city), hjust = .4, vjust = -0.5, size = 3) +
  theme_minimal() +
  labs(
    x = "N",
    y = "Average Salary"
  )

```


# Company Composition {data-orientation=columns}

```{r, echo=FALSE}
# Create a frequency table of the survey_city column
city_frequency <- table(geographic_trends_data$survey_city)

# Sort the frequency table in descending order
sorted_city_frequency <- sort(city_frequency, decreasing = TRUE)

# Get the top ten most occurring cities
top_ten_cities <- names(sorted_city_frequency[1:10])

#print(top_ten_cities)

```

## column {data-height=600}

### What types of jobs (By company) are students getting by region?  

```{r, echo=FALSE}
data = geographic_trends_data %>%
  group_by(survey_city, survey_company_cluster_name) %>%
  summarize(count=n()) %>%
  arrange(-count, survey_company_cluster_name)

custom_column_names <- c("City", "Company", "Number of Students")

datatable(data, rownames=F, extensions = 'Buttons', colnames = custom_column_names,
          options = list(dom='Bfrtip',
                         buttons=c('copy','csv','excel')
                         ),
          filter=list(position='bottom',
                      clear=F,plain=T
                      )
          )
```

## column {data-height=600}

### Are bank and consulting jobs in Chicago and NYC?

#### NYC

```{r, echo=FALSE}
geographic_trends_data$survey_city[geographic_trends_data$survey_city=="newyorkcity"] <- "NYC"
data = geographic_trends_data %>%
  filter(survey_city=="NYC" ) %>%
  group_by(survey_city, survey_company_cluster_name, survey_deptfunc, survey_salary) %>%
  summarize(count=n()) %>%
  arrange(-count, survey_company_cluster_name, survey_city)

custom_column_names <- c("City", "Company", "Job Position", "Salary", "Number of Students")

datatable(data, rownames=F, extensions = 'Buttons', colnames = custom_column_names,
          options = list(dom='Bfrtip',
                         buttons=c('copy','csv','excel')
                         ),
          filter=list(position='bottom',
                      clear=F,plain=T
                      )
          )
```

#### Chicago
```{r, echo=FALSE}
data = geographic_trends_data %>%
  filter(survey_city=="chicago") %>%
  group_by(survey_city, survey_company_cluster_name, survey_deptfunc, survey_salary) %>%
  summarize(count=n()) %>%
  arrange(-count, survey_company_cluster_name, survey_city)

custom_column_names <- c("City", "Company", "Job Position", "Salary", "Number of Students")

datatable(data, rownames=F, extensions = 'Buttons', colnames = custom_column_names,
          options = list(dom='Bfrtip',
                         buttons=c('copy','csv','excel')
                         ),
          filter=list(position='bottom',
                      clear=F,plain=T
                      )
          )
```

# Top 3-5 Companies by City {data-orientation=columns}

What are the top 3-5 job categories (by company) by city (Chicago, Cincinnati, Cleveland, Columbus)?

## row {data-height=600}

### Chicago

```{r, echo=FALSE}
data = geographic_trends_data %>%
  filter(survey_city=="chicago") %>%
  group_by(survey_city, survey_company_cluster_name) %>%
  summarize(count=n()) %>%
  arrange(-count, survey_company_cluster_name) %>%
  slice_head(n = 5)

custom_column_names <- c("City", "Company", "Number of Students")
datatable(data, rownames=F, extensions = 'Buttons', colnames = custom_column_names)
```

### Cleveland

```{r, echo=FALSE}
data = geographic_trends_data %>%
  filter(survey_city=="cleveland") %>%
  group_by(survey_city, survey_company_cluster_name) %>%
  summarize(count=n()) %>%
  arrange(-count, survey_company_cluster_name) %>%
  slice_head(n = 5)

custom_column_names <- c("City", "Company", "Number of Students")
datatable(data, rownames=F, extensions = 'Buttons', colnames = custom_column_names)
```


## row {data-height=600}


### Cincinnati

```{r, echo=FALSE}
data = geographic_trends_data %>%
  filter(survey_city=="cincinnati") %>%
  group_by(survey_city, survey_company_cluster_name) %>%
  summarize(count=n()) %>%
  arrange(-count, survey_company_cluster_name) %>%
  slice_head(n = 5)

custom_column_names <- c("City", "Company", "Number of Students")
datatable(data, rownames=F, extensions = 'Buttons', colnames = custom_column_names)
```


### Columbus

```{r, echo=FALSE}
data = geographic_trends_data %>%
  filter(survey_city=="columbus") %>%
  group_by(survey_city, survey_company_cluster_name) %>%
  summarize(count=n()) %>%
  arrange(-count, survey_company_cluster_name) %>%
  slice_head(n = 5)

custom_column_names <- c("City", "Company", "Number of Students")
datatable(data, rownames=F, extensions = 'Buttons', colnames = custom_column_names)
```
